---
title: "Lab 7"
author: "Max Ward"
date: "2/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(lubridate)
data1 <- read.table('household_power_consumption.txt', 
                    sep=";",                            
                    header = T,                        
                    na.strings = c("NA","", "?"),       
                    stringsAsFactors=FALSE
                    )
```

```{r}
data2 <- data1%>%
  separate(Date, into =c("day", "Month", "Year"))%>%
  select(Year, Voltage)%>%
  group_by(Year)
data2
```

***What was the average voltage used in each year, and what year used the most?
```{r}
data2 %>% 
  group_by(Year) %>% 
  summarise(
    avg_volts = mean(Voltage, na.rm = TRUE),
    n = n()) %>% 
  ggplot(mapping = aes(Year, avg_volts)) +
    geom_count()
```


***As we can see from the graph, 2009 used the most volts everyday on average. This was what I kind of guessed because more technoly is being used so more energy is aswell. But then dips back down in 2010 because of what I guess is because things are becoming more energy effecient.  

***I think this is an interesting question becuase more and more technology is being used over the years I would expect to see more energy used, but also things are becoming for efficient so I wanted to see where it measured up. 

***I came up with this quesrion just becuase the data allowed it and I was interesting in finding the answer. I did a lot of stuff from the last chapter and some from the new. I also did a geom line becuase I thought that was the best way to show the highes and the lowes of the data. 
